Basics of cubic spline models

### 2021-11-15 text/15/missing-values-in-r.Rmd
Added 2015.md

---
title: "PMean: Missing values in R talk"
author: "Steve Simon"
source: "http://blog.pmean.com/missing-values-in-r/"
date: "2015-02-07"
category: Blog post
tags: R software
output: html_document
---

>>>>

---
title: "PMean: Missing values in R talk"
author: "Steve Simon"
source: "http://blog.pmean.com/missing-values-in-r/"
date: "2015-02-07"
category:
- Blog post
tags:
- R software
output: html_document
---

### 2021-11-15 text/21/cubic-splines.Rmd
Added 2015.md

>>>>

```{r}
simulated_example %>%
  mutate(x1=x) %>%
  mutate(x4=(x>5)*(x-5)) %>%
  mutate(x5=(x>10)*(x-10)) %>%
  mutate(x6=(x>15)*(x-15)) -> linear_spline_basis
```

```{r}
lm(y~x1+x4+x5+x6, data=linear_spline_basis) %>%
  augment(newdata=linear_spline_basis) %>%
  ggplot(aes(x, y)) +
    geom_point() +
  geom_line(aes(y=.fitted))
```

```{r}
simulated_example %>%
  mutate(x1=x) %>%
  mutate(x2=x^2) %>%
  mutate(x4=(x>5)*(x-5)^2) %>%
  mutate(x5=(x>10)*(x-10)^2) %>%
  mutate(x6=(x>15)*(x-15)^2) -> quadratic_spline_basis
```

```{r}
lm(y~x1+x4+x5+x6, data=quadratic_spline_basis) %>%
  augment(newdata=quadratic_spline_basis) %>%
  ggplot(aes(x, y)) +
    geom_point() +
  geom_line(aes(y=.fitted))
```
